 \documentclass[10pt]{memoir}

% based on kieran healy's memoir modifications
\usepackage{mako-mem}
\chapterstyle{article-2}
\pagestyle{mako-mem}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}

%\usepackage{kpfonts}
%\usepackage[bitstream-charter]{mathdesign}
\usepackage{fbb}
\usepackage[T1]{fontenc}
%\usepackage{textcomp}

%\renewcommand{\rmdefault}{ugm}
%\renewcommand{\sfdefault}{phv}

% Packages for making a landscape table (?)
\usepackage[table,usenames,dvipsnames]{xcolor}
\usepackage{multirow, makecell}
\usepackage{pdflscape}
\usepackage{afterpage}

\usepackage[letterpaper,left=1.125in,right=1.125in,top=1.25in,bottom=1.25in]{geometry}

\usepackage{datenumber}
\setdate{2020}{8}{24}
\def\datedate{\datedayname,\space\datemonthname~\thedateday}

\newcommand{\adddays}[1]{%
    \addtocounter{datenumber}{#1}%
    \setdatebynumber{\thedatenumber}%
}

% Common packages
\usepackage{graphicx}
\usepackage{enumerate}

\usepackage{caption}
\captionsetup[table]{name=Unit}

% Setup list environments
\usepackage{enumitem}
\setlist[description]{
  topsep=0pt,
  before=\vspace{0pt},
  after=\vspace{0pt},
  itemsep=2pt,
  labelsep=0pt
}

\setlist[itemize]{
    noitemsep, 
    leftmargin=1em,
    topsep=0pt}

% Set paragraph indents and spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{.5\baselineskip}
%\usepackage[document]{ragged2e}

% adjust section title formatting
\usepackage{titlesec}
\titlespacing\section{0pt}{8pt plus 2pt minus 2pt}{-6pt}
\titlespacing\subsection{0pt}{8pt plus 2pt minus 2pt}{-6pt}
\titlespacing\subsubsection{0pt}{8pt plus 2pt minus 2pt}{10pt}

% allows full, in-line citations
\usepackage{bibentry} 

% add bibliographic stuff 
\usepackage[round, numbers]{natbib} \def\citepos#1{\citeauthor{#1}'s (\citeyear{#1})} \def\citespos#1{\citeauthor{#1}' (\citeyear{#1})}
\renewcommand{\bibnumfmt}[1]{}

% define colors from http://www.colorado.edu/brand/visual-identity/typography-color
%\usepackage[usenames,dvipsnames]{color}
\definecolor{CUGold}{RGB}{207,184,124}
\definecolor{CUDarkGray}{RGB}{86,90,92}
\definecolor{CULightGray}{RGB}{162,164,163}

% customize URLs
\usepackage[hyphens]{url}
%\usepackage{breakurl} 
\usepackage[breaklinks, bookmarks, bookmarksopen]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=Blue,
    citecolor=Black,
    filecolor=Blue,
    urlcolor=Blue,
    unicode=true,
    breaklinks=true}

% create a "reading list" environment to format the items
\newenvironment{readinglist}{
\begin{list}{}{\leftmargin=0pt \itemindent=0em}
  \setlength{\itemsep}{8pt}
  \setlength{\parskip}{0em}
  \setlength{\parsep}{1em}
  \setlength{\parindent}{8em}}
{\end{list}}

% Course/Instructor metadata -- alter as needed
\def\mycoursename{Applied Machine Learning}
\def\mycourselisting{INFO 4604/5604}
\def\myclassroom{This course will meet remotely}
\def\myzoomurl{https://cuboulder.zoom.us/j/97223801648}
\def\mycanvasurl{https://canvas.colorado.edu/courses/76472}
\def\mymeetingdays{Monday, Wednesday, Friday}
\def\mymeetingtimes{9:10AM--10:00AM}
\def\mydate{Fall 2021}

\def\instructorAfirstname{Abram}
\def\instructorAlastname{Handler}
\def\instructorAfullname{\instructorAfirstname~\instructorAlastname}
\def\instructorAtitle{Instructor, Information Science}
\def\instructorAoffice{NA}
\def\instructorAemail{abram.handler@colorado.edu}
\def\instructorAwebsite{https://www.abehandler.com/}
\def\instructorAofficehours{Wed 3PM to 4PM, and by appointment (https://cuboulder.zoom.us/my/abehander)}



\begin{document}

\nobibliography*

%\baselineskip 14.2pt

\title{
    \textbf{\huge{\mycoursename}}\\
    \vspace{5pt} \normalsize{\mycourselisting}; \mydate
}

\author{
    \mymeetingdays; \mymeetingtimes\\
    \myclassroom\\ Zoom: \href{\myzoomurl}{\myzoomurl} \\ Canvas:  \href{\mycanvasurl}{\mycanvasurl}
}

\date{
    \normalsize{
        \href{\instructorAwebsite}{\textbf{\instructorAfullname}}\\
        \instructorAtitle\\
        E-mail: \href{mailto:\instructorAemail}{\instructorAemail}\\
        %Office: \instructorAoffice\\
        Office hours: \instructorAofficehours\\\vspace{1em}
        
    }
}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%
%% Acknowledgements %%
%%%%%%%%%%%%%%%%%%%%%%
% This syllabus template was made in LaTeX by Brian Keegan and is distributed as Free Software under the GNU GPL v3. It was built using style templates created by Aaron Shaw, Benjamin Mako Hill, and Kieran Healy.


% \clearpage

\section{\textbf{Course Description}}

This course offers an applied introduction to machine learning. It focuses on using existing software tools to solve practical problems with machine learning methods. The course also presents more theoretical perspectives, with an eye towards selecting, analyzing, debugging and interpreting methods in practice. 

This course requires proficiency with Python programming; students should be comfortable learning new Python libraries with minimal support. There is no specific math requirement for the course, however students should feel comfortable with mathematical notation and quantitative reasoning. Prior exposure to concepts from probability and discrete math (e.g.\ INFO 2301) will help. 

The course offers:

\begin{itemize}
\item An introduction to foundational concepts in machine learning
\item Hands-on practice applying machine learning methods to practical problems
\item An introduction to machine learning tools in Python 
\end{itemize}

By the end of this semester you will be able to:
\begin{itemize}
\item Identify when machine learning can help solve a problem
\item Identify which approaches are appropriate for a particular problem
\item Be comfortable using standard machine learning tools in Python
\item Understand underlying concepts well enough to use and modify machine learning code
\end{itemize}

\section{\textbf{4605 vs 5604}}

Students in this class are enrolled in either 4604 (undergraduate-level) or 5604 (graduate-level). \textbf{Graduate students should be enrolled in 5604}. Undergraduates in the BAM program may also take 4604 (but check with advising first).
Students in 5604 will be assigned additional readings, as well as additional problems on homeworks, quizzes and exams.
4604 students can do the 5604 problems for extra credit.

\section{\textbf{Remote Course Policies}}
Class will meet three times per week (\mymeetingdays)\space from \mymeetingtimes\space on Zoom. There will be lectures and in-class activities during class time. \textbf{Attendance is required.} 
In order to fully participate remotely, students will need access to a personal computer with a web camera, a reliable high-speed internet connection, and a minimally disruptive background environment. 
{You will often do coding assignments during class so please join with a computer and not a phone}.
Please email the instructor immediately if you expect any issues with remote participation.

\section{\textbf{Books}}

\textbf{Required}

4604/5604: \href{https://www.packtpub.com/product/python-machine-learning-third-edition/9781789955750}{Raschka and Mirjalili (2019) Python Machine Learning, 3rd Edition}. Available as an e-book from \href{https://www.packtpub.com/product/python-machine-learning-third-edition/9781789955750}{Packt}. Earlier editions are also acceptable. Companion code is available \href{https://github.com/rasbt/python-machine-learning-book-3rd-edition}{here}.
 
\textbf{Optional}

\href{https://www.cs.ubc.ca/~murphyk/MLbook/}{Kevin Murphy, Machine Learning: a Probabilistic Perspective}. This is a standard textbook for machine learning courses, with comprehensive coverage of the field. It is useful both as an introduction and as a reference book for students who want to do research in machine learning.

\href{https://www.abehandler.com/resources/openintro-statistics.pdf}{Diez, Cetinkaya-Rundel and Barr, OpenIntro Statistics}. Available as a free e-book. This book introduces many of the mathematical concepts used in this course, and you may find it to be a helpful supplement. Material on probability may be especially useful.

\section{\textbf{Quizzes}}

This class will include many quizzes.
Quizzes will be open book.
You can use any materials from the course (or any website, though this will be not be necessary) to answer questions on a quiz. 
Because everyone sometimes has a bad day or needs more time to master a new concept, the instructor will automatically drop the lowest five quiz scores from your final grade.
If you miss a quiz question, this indicates a gap in your knowledge. You are strongly encouraged to submit a correction explaining in detail what you missed, in order to get half credit back on the quiz. 
You can submit a correction up to 1 week after the quiz.
Correction link is here: \url{https://forms.gle/YHqtTCTjsEquJ32j8}

\section{\textbf{In-class activities}}
This class will sometimes include many in-class coding activities.
You will turn in in-class activities to Canvas at the end of class.
These activities will be graded loosely based on effort and correctness (check minus, check, check plus), with an understanding that you have limited time to complete the work.
\textbf{You are not expected to work on in-class activities outside of class.}

I understand that stuff will come up during the semester. You might oversleep your alarm. Your laptop might break. You might have to take an emergency trip. So I will automatically drop your lowest 4 in-class activity scores at the end of the semester.


\section{\textbf{Attendance}}
Attendance for this class is required. 
The instructor will take attendance on random days to calculate your attendance score.
In-class activities will also be used to calculate your attendance score.

\section{\textbf{Homeworks}}
This class will have regular homeworks. 
You may complete the homeworks alone or with one partner. 
If you work with a partner, you must list the partner on your assignment. 
Homeworks will be challenging! It will be important to start early.

\section{\textbf{Final projects}}
There will be a final project, in which you apply the methods from class to your own dataset.
You will work on your final project alone, not with a group.

\section{\textbf{Late work}}
The instructor understands that students are busy with many obligations. 
Therefore, across the whole semester, you will be allotted a total of five free late days to turn in assignments. 
If you turn in an assignment within 24 hours after the deadline you will be deducted 1 late day. 
If you turn in an assignment within 48 hours after the deadline you will be deducted 2 late days, and so on. 
If you have used five or fewer late days so far during the semester (including the most recent assignment) you will not be penalized for late work. 
However, after you have used up your late days, late homework will not count for credit except in special circumstances.

\section{\textbf{Grading}}

Final grades are calculated according to the following distribution:
\begin{itemize}
\item 20\% Homework
\item 20\% In-class activities
\item 20\% Quizzes (online, via Canvas)
\item 5\% Attendance and participation
\item 25\% Final Project
\end{itemize}

Letter grades will follow a typical scoring distribution (A if >= 93\%, A- if >= 90\%, B+ if >=
87\%, B if >= 83\%, B- if >= 80\%, C+ if >= 77\%, and so on). Do not expect most grades to be
curved, though exam grades may be curved if needed.

% \subsection{Requirements}
% Students' regular and sustained participation in all class activities as well as punctual and thorough completion of assignments are essential. If you need to be excused from attending a class session or need an extension to an assignment, please \href{mailto:brian.keegan@colorado.edu}{email instructor} at least 24 hours in advance.



\section{\textbf{Computing Requirements}}
Students will need to use statistical computing software as well as teleconferencing software to participate in class. \href{http://jupyter.org/}{Jupyter notebooks} written in Python 3 will be used for all in-class examples and assignments. We will use many Python libraries such as \href{https://scikit-learn.org/}{scikit-learn}. The \href{https://www.continuum.io/why-anaconda}{Anaconda distribution} of Python 3.5 (or above) is \textit{strongly} recommended. It makes it easy to install all of the supporting libraries we will use in this course. Lectures will include exercises and presentations, with the expectation that students participate with their own computers. If students do not have access to a computer to use for computing or Zoom, they should immediately email the instructor. Students who require technical assistance should email the instructors with the code and data they are working with, a summary of their debugging efforts to date, and attend an instructor's office hours.

\clearpage

\section{\textbf{Schedule}}

This course will be divided into three units. \\

\begin{table}[htb!]
\centering
\begin{tabular}{cll}
     \textbf{Week} & \textbf{Topic} & \textbf{Method}   \\
    \cmidrule[.1em](lr){1-3}
    
     1 & Intro to machine learning &  \\
    \cmidrule[.1em](lr){1-3} 
 
     \multirow{1}{*}[0pt]{\textit{}} 
         1  & Geometry of data, bias and variance & KNN  \\ 
        \cmidrule[.1em](lr){1-3}
        
    \multirow{1}{*}[0pt]{\textit{}} 
         2  & Parameters and learning & Perceptron   \\ \cmidrule[.1em](lr){1-3}

    \multirow{1}{*}[0pt]{} 
         2 & Optimization and loss & Logistic regression \\   \cmidrule[.1em](lr){1-3}    

   \multirow{1}{*}[0pt]{} % Brian
         3 &  Regularization & Logistic regression  \\ \cmidrule[.1em](lr){1-3}             

     3 & Generative models & Naive Bayes \\
    \cmidrule[.1em](lr){1-3} 

    4  &  Train/test split, overfitting  &  All methods  \\
    \cmidrule[.1em](lr){1-3}

   4   & Non-linear prediction, ensembles  & decision trees, random forests \\
    \cmidrule[.1em](lr){1-3}

\end{tabular}\\
\caption{Introduction to ML}
\end{table}

\begin{table}[htb!]
\centering
\begin{tabular}{cll}
     \textbf{Week}  & \textbf{Topic} & \textbf{Details}   \\
    \cmidrule[.1em](lr){1-3}
    
     5  & Data creation &  Annotation and agreement \\
    \cmidrule[.1em](lr){1-3} 
 
     5  & Feature creation &  The art of feature engineering \\
    \cmidrule[.1em](lr){1-3} 

     6  & Evaluation and diagnosis &  Precision, recall, ROC AUC, confusion matrixes \\
    \cmidrule[.1em](lr){1-3} 

     6  & Review &   \\
    \cmidrule[.1em](lr){1-3} 

\end{tabular}\\
\caption{Practical ML}
\end{table}

\begin{table}[htb!]
\centering
\begin{tabular}{cll}
     \textbf{Week} & \textbf{Topic} & \textbf{Details}   \\
    \cmidrule[.1em](lr){1-3}
    
     13   & FATE &   Fairness, accountability, transparency and ethics \\
    \cmidrule[.1em](lr){1-3} 
 
     14  & Topic models &  LDA and Mallet, applications in NLP \\
    \cmidrule[.1em](lr){1-3} 

     15  & Deep learning &  Gradients, backpropagation, software packages \\
    \cmidrule[.1em](lr){1-3} 

     16   & Final presentations &   \\
    \cmidrule[.1em](lr){1-3} 
    

\end{tabular}\\
\caption{Other topics in ML}
\end{table}

\clearpage


\section{\textbf{Course Policies}}

% \subsection{Professional Expectations}
% In addition to the expectations outlined in the \href{https://www.colorado.edu/creed/}{Colorado Creed}, we expect students to conduct themselves in a professional manner in their interactions

\input{policies}

\section{\textbf{Acknowledgements}}
% The design and format of this course borrows from other courses.
% \begin{itemize}[itemsep=1em]
%     \item Bergstrom, Carl \& West, Jevin (2017). \href{http://callingbullshit.org/index.html}{\textit{Calling Bullshit}}. University of Washington.
% \end{itemize}

This syllabus was typeset in \LaTeX~using \href{http://www.sharelatex.com}{Overleaf} with the \href{http://www.tug.dk/FontCatalogue/fbb/}{fbb/Bembo} font and is derived from the \texttt{memoir} styles adapted by \href{https://github.com/kjhealy/latex-custom-kjh}{Kieran Healy} and \href{http://projects.mako.cc/source/?p=latex_mako;a=summary}{Benjamin `Mako' Hill}. It is modified from a syllabus from \href{https://www.brianckeegan.com/}{Brian Keegan}. This course follows curriculum developed by \href{https://cmci.colorado.edu/~mpaul/}{Michael J. Paul}.

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%%% COURSE OUTLINE %%%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%


\renewcommand{\bibsection}{\section{\huge \bibname}\prebibhook}
\baselineskip 14.2pt
\nobibliography{refs}
\bibliographystyle{apalike}

\end{document}